R genes

### 2022-02-21 analysis/plotRgenes.Rmd
summaryTable

---
title: "R genes"
output: html_notebook
---
```{r setup}
library(tidyverse)
library(wesanderson)
library(ggtree)
library(ggtreeExtra)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

>>>>

---
title: "R genes"
output: html_notebook
---
```{r setup}
library(tidyverse)
library(wesanderson)
library(ggtree)
library(ggtreeExtra)
library(kableExtra)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

# Quick summary stats

```{r}
df %>% group_by(Genome, Class) %>% summarise(sum=sum(Count)) %>% kbl() %>%
  kable_styling()
```
